\documentclass[conference,compsoc]{IEEEtran}

% *** CITATION PACKAGES ***
%
\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
  \usepackage[nocompress]{cite}
\else
  % normal IEEE
  \usepackage{cite}
\fi


\usepackage{amsmath}
\usepackage{algorithm, algorithmic}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{array}
\usepackage{url}
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}


\begin{document}
\title{Project 3: Influence Maximizing Problem }

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Yuejian Mo  11510511}
\IEEEauthorblockA{Department of Biology\\
Southern University of Science and Technology\\
Email: 11510511@mail.sustc.edu.cn}}

% make the title area
\maketitle

\IEEEpeerreviewmaketitle

\section{Preliminaries}
This project is an implementations of Greedy algorithm to find out a seed set
to maximize the spread of influence through a social network, based on LT(Linear
Threshold) and IC(Independent Cascade) models. With the development of Internet
and smart phone, more and more people are connected by social network. It is
interesting to study the influence spread between different members. Ecplicaty,
maximizing the spread in network with less afford takes the eyes of adversity
provider and government managers. In 2003, Kempe, Kleinberg and Tardos proposal
two models to represent and optimize this kind of problem.\cite{1}

This problem, Influence Maximizing Problem(IMP) is a NP-hard. Inspired by
above report, I success produce seed set by natural greedy.

% Add figure here

\subsection{Software}
This project is written by Python 3.7 with editor Atom and Vim. Numpy, os, time,
random, sys and argparse library are used.

\subsection{Algorithm}
Using LT and IC model to evaluate the spread influence of seed sets and natural
greedy algorithm to search optimal seeds set.


\section{Methodology}
Firstly, a social network is modeled as a directed graph $G=(V,E)$ and each
edge $(u,v)\in E$ is associated with a weight $w(u,w)=\frac{1}{d_{in}}$ which
indicates the probability that $u$ influences $v$. $S\in V$ is the subset of
nodes selected to initiate the influence diffusion,  which is called seeds set.

Then, I try to evaluate the spread influence with two different diffusion
models. In \textit{Linear Threshold} model, a node $v$ is influenced by each
neighbor $u$ according to a weight $w_{v,u}$ such that $\sum_{u}{w_{v,u}}
<=1$. The dynamics is following. Each node $v$ are accessed a threshold $\theta\in
[0,1]$ randomly obeyed uniform distribution at first step; this represents
the weighted fraction of $v$' neighbors that must become active in order
for $v$ become active. In step $t$, each inactive node $v$ will be active
by its active neighbors $w$ at step $t-1$ as following
$$\sum_{w}{w_{u,v}} >= \theta_v$$. Once no new active node is generated,
maximal spread influence will obtain with given seeds set in specified graph.
I notices final influence as the total number of active node $\sigma$.

In \textit{Independent Cascade} model, I start with an initial set of active
nodes $S$, and the process unfolds in discrete steps according to the following
randomized rule. When node $v$ first becomes active in step $t$, it is given
a single chance to activate each currently inactive neighbor $w$; it succeeds
with a probability $w_{v,w}$, independently of the history thus far. Every
step. In practical, for each inactive neighbor $w$ of new active node $v$ will
be active, if $w_{v,w}$ is larger than a new generated random number between 0 and
1 obeyed uniform distribution. (If $w$ has multiple newly activated neighbors,
their attempts are sequenced in an arbitrary order.) If $v$ succeeds, then it
cannot make any further attempts to activate $w$ in subsequent rounds. Again,
the process runs until no more activation are possible.

Both of Linear Threshold and independent Cascade model are stimulated by
repeating many time to average influence for each seed.

Finally, the seed required for IMP is generated by a natural greedy algorithm.
Each time, a node with highest influence will added to a seeds set. This empty
seed set will fill with $k$ node, where $k$ is given from outside.

\subsection{Representation}
Some main data are maintain during process: \textbf{time\_budget},
\textbf{node\_num}, \textbf{graph\_cp}, \textbf{graph\_pc}, \textbf{incoming}.
Others data would be specified inside functions.

\begin{itemize}
  \item \textbf{time\_budget}: How many second (in Wall clock) spend on instance,
	  which provided from OJ system.
  \item \textbf{node\_num}: The total node number of given graph.
  \item \textbf{graph\_cp}: The adjacent list of network graph using dictionary,
	  where a node point to all precursors, which is generated from input file.
  \item \textbf{graph\_pc}: The adjacent list of network graph using dictionary,
	  where a node point to all descendants, which is generated from input
		file.
  \item \textbf{incoming}: A dictionary stores the incoming weight $w_{v,u}$,
	  indexed by node $u$.
\end{itemize}


\subsection{Architecture}
Here list all functions of \textbf{ISE.py} in given code:
\begin{itemize}
    \item \textbf{genSeeds}: Read seeds and store in a list from input file.
    \item \textbf{genGraph}: Generate $graph\_cp$ and $graph\_pc$ from input file.
    \item \textbf{LT}: Calculate influence of linear threshold model of given seeds
	    set.
    \item \textbf{IC}: Calculate influence of independent cascade model of given
	    seeds set.
    \item \textbf{calSpread}: Calculate influence by repeating many time of $LT$
	    or $IC$ function.
    \item \textbf{s\_format}: Standard output function. 
    \item \textbf{\_\_main\_\_}: Main control function. 
\end{itemize}
The \textbf{IMP.py} is similar to \textbf{ISE.py}, but one function is added:
\begin{itemize}
    \item \textbf{hill\_greedy}: Find out optimal seeds set using Hill-Greedy
	    algorithm.
\end{itemize}

The \textbf{ISE.py} and \textbf{IMP.py} were executed in OJ system and local
system.

\subsection{Detail of Algorithm}
Here describes some vital functions.
\begin{itemize}
    \item \textbf{genGraph}: Generate global cost and demand graph from
    input file.
    \begin{algorithm}[H]
     \caption{genGraph}
     \begin{algorithmic}[1]
     \renewcommand{\algorithmicrequire}{\textbf{Input:}}
     \renewcommand{\algorithmicensure}{\textbf{Output:}}
     \REQUIRE $input\_file\_name$
     \ENSURE $graph\_cp, graph\_pc, incoming$
     \STATE open $input\_file\_name$ as $file$ \COMMENT{open file and read line
     by line}
     \STATE $node\_num$, $edge\_num$ $\leftarrow$ first line of $file$
     \STATE \COMMENT{Read each line information until arrive edge information}
     \FOR {each line in $file$}
       \STATE $precursor$,$descendant$,$weight$ $\leftarrow$ split each line
          \STATE $graph\_cp[precursor] = descendant$
	  \STATE $graph\_pc[descendant] = precursor$
	  \STATE $incoming[descendant] = weight$
     \ENDFOR
     \end{algorithmic}
   \end{algorithm}

   \item \textbf{LT}: Calculate the influence of seeds set of Linear Threshold
	   model.
     \begin{algorithm}[H]
     \caption{LT}
     \begin{algorithmic}[2]
     \renewcommand{\algorithmicrequire}{\textbf{Input:}}
     \renewcommand{\algorithmicensure}{\textbf{Output:}}
     \REQUIRE $graph\_pc, S, incoming$
     \ENSURE  length of $isActive$
     \STATE copy $S$ to new list $isActive$
     \STATE create empty list $threshold$
     \FOR { each node in graph}
	\STATE Add Random Number $\alpha$ between [0,1] to $threshold$
	\IF {$\alpha == 0$}
	     \STATE add this node to $isActive$
	\ENDIF
     \ENDFOR
     \STATE $saturation \leftarrow 0$ 
     \STATE $lastlen \leftarrow $ length of $isActive$ 
     \WHILE{ NOT $saturation$ }
	\STATE $pulse \leftarrow 0$
        \FOR {each inactive node $v$ \AND $s$'s precursor is active}
	     \STATE $pulse \leftarrow incoming[v]$
        \ENDFOR
	\IF {$pulse \le threshold[v]$}
            \STATE add node $v$ to $isActive$
	\ENDIF
	\IF {$lastlen ==$ length of $isActive$}
	     \STATE $saturation \leftarrow 1$ 
	\ENDIF
	\STATE $lastlen \leftarrow$ length of $isActive$
     \ENDWHILE
     \RETURN length of $isActive$
     \end{algorithmic}
     \end{algorithm}

  \item \textbf{IC}: Calculate influence of seeds set of Independent
	 Cascade model.
    \begin{algorithm}[H]
     \caption{IC}
     \begin{algorithmic}[3]
     \renewcommand{\algorithmicrequire}{\textbf{Input:}}
     \renewcommand{\algorithmicensure}{\textbf{Output:}}
     \REQUIRE $graph\_cp, S, incoming$
     \ENSURE  length of $isActive$
     \STATE copy $S$ to $isActive$ and $lastActive$ 
     \STATE $balance \leftarrow 0$
     \WHILE { NOT $balance$}
	\STATE create empty list $newActive$
	     \FOR{each active node $v$'s inactive neighbor $w$}
		\IF{ $incoming[w] \le$ RANDOM NUMBER $alpha$ }
		    \STATE add $w$ to $newActive$
		    \STATE add $w$ to $isActive$
		\ENDIF
	     \ENDFOR
            \IF{length of $newActive$ == 0 OR  length of $isActive$ == $node\_num$}
	     \STATE $balance \leftarrow  1 $
	     \ENDIF
     \ENDWHILE
     \RETURN length of $isActive$
     \end{algorithmic}
     \end{algorithm}
 
 \item \textbf{hill\_greedy}: Generate optimal seed using Hill Greedy Algorithm
     \begin{algorithm}[H]
     \caption{hill\_greedy}
     \begin{algorithmic}[4]
     \renewcommand{\algorithmicrequire}{\textbf{Input:}}
     \renewcommand{\algorithmicensure}{\textbf{Output:}}
     \REQUIRE $size, model$
     \ENSURE  $seeds$
     \STATE create empty $ans\_seeds$
     \STATE $cnt \leftarrow 0$
     \WHILE{$cnt \ne size$}
	\STATE copy $ans\_seeds$ to $cur\_seed$
	\STATE $high \leftarrow 0$
	\STATE $point \leftarrow 1$
        \FOR{each node $4$ don't be chosen}
	     \STATE add $v$ to $cur\_seed$
	     \IF{$model$ == IC}
	          \STATE $new\_high \leftarrow IC(graph\_pc,cur\_speed, incoming)$ 
	     \ELSE
	          \STATE $new\_high \leftarrow LT(graph\_cp,cur\_speed, incoming)$ 
	     \ENDIF
	     \IF{$nw\_high \le high$}
	         \STATE $high \leftarrow new\_high$
		 \STATE $point \leftarrow v$
	     \ENDIF
        \ENDFOR
	\STATE add $point$ to $ans\_seeds$
	\STATE $cnt \leftarrow cnt+1$
     \ENDWHILE
     \RETURN $ans\_seeds$
     \end{algorithmic}
     \end{algorithm}
 

\end{itemize}


\section{Empirical Verification}
Empirical verification is confirmed in OJ system. $ISE.py$ almost pass all
dataset with reasonable bias. $IMP.py$ only was test with network-5-IC and
provide reasonable seeds set.

\subsection{Design}
Independent cascade model return reasonable influence is small graph and big graph.
But Linear Threshold model return less reasonable due with large graph. Finally,
I found my code would added some element repeatedly result in larger bias.

For hill greedy, because I just evaluate once, it produce seeds set fast. In
small graph, which produce seeds in 65 percent effect. But
Not optimal seeds are produced every time.

\subsection{Data and data structure}
Dictionaries and lists are used widely rather than matrix. Because the input graph
is sparse, dictionary are always used to store graph as adjacent list. Global
variable $graph\_pc$, $graph\_cp$ and $incoming$ are dictionary. Lists always
store routes and edges information for local variable.

\subsection{Performance}
Following table show different performance with different dataset. Offline
test perform at Fedora 29 with $Intel^{®}$ Xeon(R) CPU E5-1680 v3@3.20GHz and
32GiB memory.

\begin{center}
   \begin{tabular}{| l | l | l |}
   \hline
    Dataset             &Run Time(s)   &Result   \\ \hline
    network-seeds-IC     & 23.23        & 5.015  \\
    network-seeds-LT     & 23.23        & 5.015  \\
    network-seeds2-IC    & 23.24        & 30.47  \\ 
    network-seeds2-LT    & 57.79        & 37.03  \\
    NetHEPT-5seeds-LT    & 58.55        & 341.9  \\
    NetHEPT-5seeds-IC    & 27.87        & 276.3  \\
    NetHEPT-50seeds-LT    &         &   \\
    NetHEPT-50seeds-IC    & 27.87        & 1003  \\
    network-5-IC         & 0.73         & 19.45  \\
   \hline
   \end{tabular}
\end{center}

\subsection{Result}
Solutions are accepted most all public dataset' test. But Linear Threshold model
produce influence with large bias. 

\subsection{Analysis}
Because natural Hill Greedy is kind of greedy algorithm without heuristics, most
of solutions are not optimal. During using adjacent list rather than adjacent
matrix, space cost is more lower than $O(n^2)$. Because every point only is
evaluate once, only less time it cost. Total, no more than $O(n^2)$ is required.

\section*{Acknowledgment}
Thanks TA Yao Zhao who explain question and provide general method to solve it.
And I also thanks for Kebing Sun discuss and share the idea about algorithm.

\bibliographystyle{IEEEtran}
\begin{thebibliography}{1}
\bibitem{1}
Kempe D, Kleinberg J, Tardos É. Maximizing the spread of influence through a
social network[C]//Proceedings of the ninth ACM SIGKDD international conference
on Knowledge discovery and data mining. ACM, 2003: 137-146.

\end{thebibliography}

% that's all folks
\end{document}


